\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-11-01 paper.tex
update

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g. unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}). In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

These deliberate deviations, termed \emph{plan-deviation attacks}, have been previously identified and tackled in the literature \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi} \zyang{add most recent articles}. These works initial solution for grid-world configuration, where robots is tasked perform inter-robot observations (usilizing the onboard sensing capabilities) as an additional security measure. Each robot' self-report includes not only its own status, but also additional observations of other robots' status. For example, robot $i$'s self-report may include its observation of robot $j$, ``$i$ report its arrival at $v$ and $i$ observes $j$ at location $w$''. Similarly, robot $j$ also reports its observations of robot $i$ to the CE \cite{wardega2019resilience}. This solution provides paths with an observation schedule such that any attempts by a compromised robot to violate the safety constraints would necessarily break the observation plan and be detected.

When transforming the solution to continuous configuration spaces, additional analysis is needed on the reachability of robots in order for the security of co-observation schedule to hold. More broadly, the problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.  This constraint is formulated using an ellipsoidal bound of the reachability region, and the idea of using an ellipsoidal bound to limit the search space is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm.

We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule.  The idea is inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm; in that case, an ellipsoidal bound is used to limit the search space with the initial and goal states fixed. In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region. We propose a mathematical formulation of reachability regions that is compatible with the solver from \zyang{cite ADMM} as a spatio-temporal constraint.

A preliminary version of the paper was presented at conferences \zyang{cite CDC IROS}. This paper extend the previous works by fixing two main challenges identified in \cite{wardega2023hola} \zyang{previous works}. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path. Agent 3 in the Figure \zyang{ref fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas. Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \zyang{ref fig:trajectories-more-constraint} and \zyang{ref fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots. This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.

>>>>

\section{Introduction}\label{sec:introduction}
%Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g. unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}). In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses the specific scenario in which attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We define these restricted regions as \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.

We focus on countering deliberate deviations, termed \emph{plan-deviation attacks}, identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}. As a security measure, robots perform inter-robot observations using their onboard sensing capabilities. Each robot's self-report includes its own status and additional observations of other robots' status. This mutual observation and reporting establish an observation schedule for the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.

In this paper, we transform the solution to continuous configuration spaces, allowing for more flexible objectives. We provide additional analysis on the reachability of robots to ensure the security of the co-observation schedule. Solving the path optimization problem with constraints based on the sets of locations that the agents could potentially reach, referred to as \emph{reachability regions}, is a novel contribution to the literature.

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. Our proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.

In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold. This problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm, we use an ellipsodial bound to limit the search space and formulated the ellipsoid as the reachability region constraint. In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region. We propose a mathematical formulation of reachability regions that is compatible with the solver from  as a spatio-temporal constraint.

This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi,yang2021multi}. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path. Agent 3 in the Figure \zyang{ref fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas. Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \zyang{ref fig:trajectories-more-constraint} and \zyang{ref fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots. This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.
